---
title: "Data Science Website"
format: html
editor: visual
---

## Data Science Questions

1.  What do you think being a data scientist is about?

Being a data scientist to me seems like a collaboration between computer science and statistics. It's about being able to manipulate, visualize, interpret and communication data.

2.  What differences/similarities do you see between data scientists and statisticians?

-   Similarities between data scientists and statisticians

-   Both have a similar skill set, including programming languages, mathematicals skills, and knowledge of statistics

-   Differences between data scientists and statisicians

-   Statisticians seem to be more in the process of designing studies and the methology of a research project where as a data scientist gets more in the weeds of the data.

-   A data scientist seems more multi-faceted

3.  How do you view yourself in relation to these two areas?

I would view myself closer to a statistician as alot of the work I do has to do with setting up research and data collection and analysis to come up with strategic strategies.

## R Code

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)
```

In the first block of text, I identify the class, type and structure of object y.

```{r}
#| echo: false
y <- density(iris$Petal.Width)
plot(y)
```

In the second block of text, I plot variable y.
